Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: example waveform

In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
the ParSpec implementation of each theory and give credit to the papers
which calculated the QNMs.

>>>>

In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for the case of the cubic EFT
of gravity include the leading-order $n = 0$ deformations to the fundamental QNM.

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
\caption{(Color online).~Example of an waveform.}
\label{fig:example_waveform}
\end{figure}
